Taking Conditional Independence Seriously:\\A Latent Network Approach to Dyadic Analysis

### 2017-10-27 paper/4_app.tex
tiny detritus removed

The re-estimation of \citet{weeks:2012} likely has the sharpest divergence between the GLM results and those of the AME Model. In Weeks' initial models,  she finds that machines are less prone to initiate conflict than the reference category, whereas Juntas, Bosses and Strong-men are more conflict-prone. When we examine the AME results, we find that none of these values are distinguishable from zero. Similarly, we find less pronounced effects for military capabilities. One explanation for this divergence is the AME model's ability to account for third order effects. Inspection of the multiplicative effects in Figure~\ref{fig:weekscirc} reveals a number of clusters of states which exhibit structural equivalence---in the top left corner we see states like the US, the UK, Germany, Canada and Israel. These states cluster together in the outer ring of this visualization because they tend to send conflicts to similar targets.\footnote{For details on how to interpret this type of visualization see \citet{minhas:etal:2016:arxiv}.} Conversely, in the bottom right of the outer ring, we see a cluster of authoritarian countries like Iraq, Russia, Syria, North Korea, and China. In the inner ring, the proximity of countries is determined by the degree to which they receive conflict from the same countries. In general, the clusters found on both the inner and outer rings have similar governmental types (Iraq, Syria, Libya, and North Korea all fell under the ``boss" category). In the GLM, which ignores these third order dependencies, many of these results might have been attributed to regime type. Structural equivalence is present even when accounting for nodal characteristics like regime type.  The AME model, on the other hand, shows that this can be specified in terms of the interdependencies captured by the multiplicative effects.

>>>>

The re-estimation of \citet{weeks:2012} has the sharpest divergence between the GLM results and those of the AME Model. In Weeks' initial models,  she finds that machines are less prone to initiate conflict than the reference category, whereas Juntas, Bosses and Strong-men are more conflict-prone. When we examine the AME results, we find that none of these values are distinguishable from zero. Similarly, we find less pronounced effects for military capabilities. One explanation for this divergence is the AME model's ability to account for third-order effects. Inspection of the multiplicative effects in Figure~\ref{fig:weekscirc} reveals a number of clusters of states which exhibit structural equivalence---in the top left corner we see the US, the UK, Germany, Canada and Israel. These states cluster together in the outer ring of this visualization because they tend to send conflicts to similar targets.\footnote{For details on how to interpret this type of visualization see \citet{minhas:etal:2016:arxiv}.} Conversely, in the bottom right of the outer ring, we see a cluster of authoritarian countries: Iraq, Russia, Syria, North Korea, and China. In the inner ring, the proximity of countries is determined by the degree to which they receive conflict from the same countries. In general, the clusters found on both the inner and outer rings have similar governmental types (Iraq, Syria, Libya, and North Korea all fell under the ``boss" category). In the GLM, which ignores these third-order dependencies, many of these results might have been attributed to regime type. Structural equivalence is present even when accounting for nodal characteristics like regime type.  The AME model, on the other hand, shows that this can be specified in terms of the interdependencies captured by the multiplicative effects.
